### 2025-01-26 my_paper/manuscript_tab_fig.tex
ref comments

% first
\begin{subfigure}{.9\textwidth}
\caption{Skin Tone Implicit Association Bias Over Time}
\centering
\includegraphics[width=.9\linewidth]{figure/Bias_twostates.png} 
\label{fig:skiniat}
\end{subfigure}
% Second
\begin{subfigure}{.9\textwidth}
\caption{Self-reported Asian Identity Over Time}
\centering
\includegraphics[width=.9\linewidth]{figure/Bias_twostates-asian.png} 
\label{fig:Asian-twostates}
\end{subfigure}
\caption*{\footnotesize{These two panels show the trends in implicit bias (panel a) and self-reported Asian identity among Asian immigrants (panel b) of the least and most biased places in the data. The District of Colombia is the least biased geographical area, and North Dakota is the most biased. The bias units are in standard deviations. Self-reported Asian identity is among first, second, and third-generation Asian immigrants aged 17 and younger still living in intact families.\\
Bias data is from the 2004-2021 Harvard's Project Implicit Association Test scores, American National Election Studies (ANES), and state-level hate crimes against Asians. Identity data is from the 2004-2021 Current Population Survey (CPS).}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[H]
\caption{Maps of State-level Implicit Association Test Bias Over Time Measure with Census Division Regional Boundaries}
\label{fig:skiniat-maps}
% first
\begin{subfigure}{.45\textwidth}
\caption{State-level Bias in 2004}
\centering
\includegraphics[width=0.9\linewidth]{figure/2004skinmap.png} 
\label{fig:skiniat-map-2004}
\end{subfigure}
\hfill%
% Second
\begin{subfigure}{.45\textwidth}
\caption{State-level Bias in 2008}
\centering
\includegraphics[width=0.9\linewidth]{figure/2008skinmap.png} 
\label{fig:skiniat-map-2006}
\end{subfigure}
\hfill%
% third
\begin{subfigure}{.45\textwidth}
\caption{State-level Bias in 2012}
\centering
\includegraphics[width=0.9\linewidth]{figure/2012skinmap.png} 
\label{fig:skiniat-map-2008}
\end{subfigure}
\hfill%
% fourth
\begin{subfigure}{.45\textwidth}
\caption{State-level Bias in 2016}
\centering
\includegraphics[width=0.9\linewidth]{figure/2016skinmap.png} 
\label{fig:skiniat-map-2010}
\end{subfigure}

>>>>

% first
\begin{subfigure}{.9\textwidth}
\caption{Bias Over Time}
\centering
\includegraphics[width=.9\linewidth]{figure/Bias_twostates.png} 
\label{fig:skiniat}
\end{subfigure}
% Second
\begin{subfigure}{.9\textwidth}
\caption{Self-reported Asian Identity Over Time}
\centering
\includegraphics[width=.9\linewidth]{figure/Bias_twostates-asian.png} 
\label{fig:Asian-twostates}
\end{subfigure}
\caption*{\footnotesize{These two panels show the trends in bias (panel a) and self-reported Asian identity among Asian immigrants (panel b) of the least and most biased places in the data. The District of Colombia is the least biased geographical area, and North Dakota is the most biased. The bias units are in standard deviations. Self-reported Asian identity is among first, second, and third-generation Asian immigrants aged 17 and younger still living in intact families.\\
Bias data is from the 2004-2021 Harvard's Project Implicit Association Test scores, American National Election Studies (ANES), and state-level hate crimes against Asians. Identity data is from the 2004-2021 Current Population Survey (CPS).}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[H]
\caption{Maps of State-level Association Test Bias Over Time Measure with Census Division Regional Boundaries}
\label{fig:skiniat-maps}
% first
\begin{subfigure}{.45\textwidth}
\caption{State-level Bias in 2004}
\centering
\includegraphics[width=0.9\linewidth]{figure/2004skinmap.png} 
\label{fig:skiniat-map-2004}
\end{subfigure}
\hfill%
% Second
\begin{subfigure}{.45\textwidth}
\caption{State-level Bias in 2008}
\centering
\includegraphics[width=0.9\linewidth]{figure/2008skinmap.png} 
\label{fig:skiniat-map-2006}
\end{subfigure}
\hfill%
% third
\begin{subfigure}{.45\textwidth}
\caption{State-level Bias in 2012}
\centering
\includegraphics[width=0.9\linewidth]{figure/2012skinmap.png} 
\label{fig:skiniat-map-2008}
\end{subfigure}
\hfill%
% fourth
\begin{subfigure}{.45\textwidth}
\caption{State-level Bias in 2016}
\centering
\includegraphics[width=0.9\linewidth]{figure/2016skinmap.png} 
\label{fig:skiniat-map-2010}
\end{subfigure}

### 2025-01-26 output/tables/tab04-regression_tab_bygen_skin.tex
ref comments

\begin{table}[!h]

\caption{Relationship Between Bias and Self-Reported Asian Identity: By Generation \label{regtab-bygen-01}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ All Gens \\ $H_{ist}$} & \specialcell{(2) \\  First Gen \\ $H^1_{ist}$} & \specialcell{(3) \\  Second Gen \\ $H^2_{ist}$} & \specialcell{(4) \\  Third Gen \\ $H^3_{ist}$}\\
\midrule
Bias & -0.26*** & -0.12 & -0.45*** & -0.43***\\
 & (0.06) & (0.08) & (0.09) & (0.11)\\
Female & 0.00 & -0.02*** & 0.00 & 0.00\\
 & (0.00) & (0.01) & (0.00) & (0.01)\\
College Graduate: Mother & 0.00 & -0.01 & 0.01 & 0.01\\
 & (0.01) & (0.01) & (0.01) & (0.01)\\
College Graduate: Father & 0.01* & 0.02** & 0.01 & -0.01\\
 & (0.00) & (0.01) & (0.01) & (0.01)\\
\midrule
Observations & 268,677 & 31,586 & 167,709 & 69,382\\
Mean & 0.65 & 0.47 & 0.23 & 0.66\\
Year $\times$ Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of a heterogeneous effect of regression (\ref{eq:identity_reg_bias}) by 
                      generation with region × year fixed effects. 
                      I include controls for sex, quartic age, fraction of Asians in a state, and parental education.
                      I also added parents' (HH, HW, and WH) and grandparents' (HHHH, HHHW, HHWH, etc.) type dummy variables to the regression
                      on second and third generation immigrants, where H is objectively Asian (born in a Asian country) and W is objectively White (native-born). 
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include children ages 17 and below who live in intact families. 
                      First-generation Asian immigrant children that were born in a 
                      Asian country. Native-born second-generation Asian 
                      immigrant children with at least one parent born in a Asian 
                      country. Finally, native-born third-generation Asian immigrant children 
                      with native-born parents and at least one grandparent born in a Asian country.}
\item[3] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{table}[!h]
\centering\centering
\caption{Relationship Between Bias and Self-Reported Asian Identity: By Generation \label{regtab-bygen-01}}
\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ $A_i$} & \specialcell{(2) \\ $A^1_i$} & \specialcell{(3) \\ $A^2_i$} & \specialcell{(4) \\ $A^3_i$}\\
\midrule
Bias & -0.09*** & -0.05 & -0.08** & -0.08**\\
 & (0.03) & (0.04) & (0.03) & (0.03)\\
Female & -0.01* & -0.01 & 0.00 & -0.01\\
 & (0.00) & (0.01) & (0.00) & (0.01)\\
College Graduate: Mother & 0.01 & -0.01 & 0.01 & 0.03\\
 & (0.01) & (0.01) & (0.01) & \vphantom{1} (0.02)\\
College Graduate: Father & 0.01** & 0.02** & 0.00 & -0.01\\
 & (0.01) & (0.01) & (0.01) & (0.02)\\
\midrule
Observations & 129,078 & 15,499 & 80,137 & 33,442\\
Mean & 0.65 & 0.44 & 0.22 & 0.66\\
Year $\times$ Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of a heterogeneous effect of regression (\ref{eq:identity_reg_bias}) by 
                      generation with region × year fixed effects. 
                      I include controls for sex, quartic age, fraction of Asians in a state, and parental education.
                      I also added parents' (AA, AW, and WA) and grandparents' (AAAA, AAAW, AAWA, etc.) type dummy variables to the regression
                      on second and third generation immigrants, where A is objectively Asian (born in a Asian country) and W is objectively White (native-born). 
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include children ages 17 and below who live in intact families. 
                      First-generation Asian immigrant children that were born in a 
                      Asian country. Native-born second-generation Asian 
                      immigrant children with at least one parent born in a Asian 
                      country. Finally, native-born third-generation Asian immigrant children 
                      with native-born parents and at least one grandparent born in a Asian country.}
\item[3] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

### 2025-01-26 output/tables/tab47-marriage.tex
ref comments

\begin{table}[H]
\centering\centering
\caption{Relationship Between Bias and Interethnic Marriages \label{regtab-logit-02}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Asian Men} & \multicolumn{1}{c}{Asian Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interethnic} & \specialcell{(2) \\ Interethnic} & \specialcell{(3) \\ Interethnic}\\
\midrule
Bias & $0.04$*** & $-0.01$ & $0.03$**\\
 & ($0.01$) & ($0.01$) & ($0.01$)\\
College Graduate: Wife & $0.04$*** & $0.04$*** & $0.05$***\\
 & ($0.00$) & ($0.01$) & \vphantom{1} ($0.00$)\\
College Graduate: Husband & $-0.01$* & $-0.01$ & $-0.02$***\\
 & ($0.00$) & ($0.01$) & ($0.00$)\\
\midrule
Observations & $69,800$ & $52,103$ & $60,214$\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interethnic}) as a
                      linear probability model.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Logistic Regression Analysis of Bias and Interracial Marriages \label{regtab-logit-03}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Asian Men} & \multicolumn{1}{c}{Asian Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interethnic} & \specialcell{(2) \\ Interethnic} & \specialcell{(3) \\ Interethnic}\\
\midrule
Bias & $0.38$*** & $-0.19$ & $0.33$**\\
 & ($0.11$) & ($0.16$) & ($0.14$)\\
College Graduate: Wife & $0.35$*** & $0.44$*** & $0.56$***\\
 & ($0.04$) & ($0.06$) & \vphantom{1} ($0.05$)\\
College Graduate: Husband & $-0.06$ & $-0.03$ & $-0.15$***\\
 & ($0.04$) & ($0.06$) & ($0.05$)\\
\midrule
Observations & $69,800$ & $52,032$ & $60,171$\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interethnic}) as a
                        logistic regression. The coefficients are exponentiated, thus should be interpreted as odds ratios.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2025-01-26 submissions/01-jope/manuscript_main.tex
ref comments

I explore how individual characteristics and social attitudes toward Asians affect self-reported Asian identity. I use identity and ancestry information from the Current Population Survey (CPS) along with a proxy for state-level bias using Harvard's Project Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes committed against Asians. \footnote{The IAT data is retrieved from Harvard's Project Implicit \autocite{greenwaldMeasuringIndividualDifferences1998}. The implicit bias toward minorities, as measured by IAT, is widely used by psychologists and is growing in use among economists. IAT scores were shown to be correlated with economic outcomes \autocite{chettyRaceEconomicOpportunity2020,gloverDiscriminationSelfFulfillingProphecy2017}, voting behavior \autocite{friesePredictingVotingBehavior2007}, and health \autocite{leitnerRacialBiasAssociated2016}.} I motivate my analysis with a simple model in the vein of \textcite{akerlofEconomicsIdentity2000}. The model makes an explicit path through which actions affect individuals' utility via their identity and introduces an externality where the actions of others---or prejudice---have different effects on a person's well-being and identity. Therefore, if a person can choose their identity credibly, and this choice is affected by the prejudice of others, then they will choose it to maximize their outcomes.

@@

Among individuals of Asian ancestry, I find that higher state-level bias---against Asians---is correlated with a lower self-reported Asian identity among Asian immigrants. I find that an increase of one standard deviation in bias correlates with a statistically significant 9 percentage point decrease in the self-reported Asian identity among first-generation immigrants, a statistically insignificant 5 percentage point decrease among second-generation immigrants, and a statistically significant 8 percentage point decrease in the self-reported Asian identity among third-generation immigrants. Additionally, a one standard deviation increase in bias is correlated with a 5 percentage points (insignificant) drop in self-reported Asian identity among second-generation Asian children with both parents born in a Asian country, a 15 percentage point decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage point decrease in self-reported Asian identity among children of White fathers-Asian mothers. Consequently, as the more economically successful Asian immigrants---educated and wealthy immigrants---may self-report Asian identity, economic research using subjective ethnic measures will underestimate White-Asian gaps in the most biased states.

@@

I use Asian implicit association test data to construct a proxy of state-level prejudice \autocite{greenwaldMeasuringIndividualDifferences1998}. This measure has been used in the social sciences, especially in psychology. Previous work has shown that IAT test scores are hard to manipulate \autocite{egloffPredictiveValidityImplicit2002}.

@@

Lastly, I incorporate data from the Uniform Crime Reports (UCR) to quantify state-level hate crimes against Asians \autocite{ucrbook}. Hate crime data offers a tangible measure of racially motivated aggression and discrimination, which, when combined with implicit and explicit bias measures, allows for a fuller understanding of the landscape of prejudice across states. This combination of implicit and explicit bias measures, along with hate crime statistics, offers a multidimensional approach to understanding the nature and prevalence of racial prejudice.

Moreover, to reduce attenuation bias and measurement error, I follow \textcite{lubotskyInterpretationRegressionsMultiple2006} in constructing a composite bias measure using  the IAT, the ANES racial animus measure and hare crimes against Asians.\footnote{More on the method in the Data Online Appendix, see Section~\ref{sub:lw-bias}.} Figure (\ref{fig:skiniat}) shows a graphical representation of the bias measure over time in the most and least biased locations. Figure (\ref{fig:Asian-twostates}) shows a graphical representation of self-reported Asian identity in the two most and least biased locations. A lower score implies less bias, whereas a higher score implies higher racial animus. A one standard deviation increase in bias is equivalent to moving from Washington, DC, or Vermont to North Dakota in 2020. I also show the state-level average bias over time in the maps in Figure (\ref{fig:skiniat-maps}) and the overall average from 2004 to 2021 in Figure (\ref{fig:iat-map-all}).
\section{Estimation and Results}\label{sec:empstrat}

To understand the association between Asian self-identity and state-level bias, I estimate regressions of the following form for each generation $g$:

@@

Where $A_{ist}^g$ be the self-reported Asian identity of person $i$ in state $s$ at the time of interview $t$, let $Bias_{st}$ be the average state-level bias in state $s$ at time $t$, $DadCollegeGrad_{ist}$, and $MomCollegeGrad_{ist}$ are indicator variables that are equal to one if the father or mother graduated from college, $Women_{ist}$ is an indicator variable for sex, and $X_{ist}$ is a vector of controls.\footnote{The controls include quartic age, fraction of population that is Asian in state $s$, type of parents (WA, AW, or AA), type of grandparents (AAAA, AAAW, etc.), and dummy variables the generation to which person $i$ belong.} Additionally, $\gamma_{rt}$ is region-time fixed effects that controls for region $\times$ year specific shocks.\footnote{I do not include state fixed effects because of lack of with-in state variation in bias.} The region $\times$ year also controls for systematic differences between regions in the overall Asian population and bias toward Asians, even if they vary over time. Throughout the analysis, I cluster the standard errors at the state level to account for correlation in the error term $\varepsilon_{ist}$ within a state, overtime.

Since the specification includes region $\times$ year, $\gamma_{rt}$, the $\beta_1^g$ coefficient summarizes individual's $i$ responsiveness to state-level bias changes in the state which they live. In other words, $\beta_1^g$ captures the association between self-reported Asian identity and state-level bias across states within a Census division region. Additionally, the $\gamma_{rt}$ fixed effects account for any regional and national trends in bias over time. Consequently, $\beta_1^g$ provide the correlation between self-reported Asian identity and state-level bias above and beyond the national and regional trends in bias. If individuals in states within a region responded similarly to changes in state-level bias, then $\beta_1^g$ will be equal to zero.

\section{Results}\label{sec:results}
The results from the regression framework described above provide consistent evidence aligning with the following findings. First, state-level bias is negatively associated with self-reported Asian identity. Second, first- and second-generation Asian immigrant children of endogamous marriages' self-reported Asian identity are more negatively associated with state-level bias.

I report the main results of estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}). I present the results of estimating the main specification for second-generation immigrants in panel (A) and for sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that bias and self-reported Asian identity are negatively associated. A one standard deviation increase in state-level bias is associated with a 9 percentage points decrease in self-reported Asian identity. Among first- and second-generation Asian immigrants, a one standard deviation increase in state-level bias is associated with 5 and 8 percentage points decrease in self-reported Asian identity. The coefficient is not statistically significant for first-generation, but the confidence interval is mostly in the negative territory. Finally, among third-generation Asian immigrants, a one standard deviation increase in state-level bias is associated with a 8 percentage points decrease in self-reported Asian identity.

I report the results of the same regression but on sub-samples of second-generation immigrants by type of parents---interracial and endogamous parents---in Figure (\ref{plot01-regression-byparent}). I present the results of estimating the main specification on second-generation immigrants in panel (A) and on sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that children of interracial parents marriages are more influenced by state-level bias. I find that a one standard deviation increase in state-level bias is associated with a 5 percentage points decrease in self-reported Asian identity among children of endogamous parents---the estimate is statistically insignificant. However, a one standard deviation increase in state-level bias is associated with a 15 percentage points decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage points decrease in self-reported Asian identity among children of White fathers-Asian mothers.

I also report the results of the regression on sub-samples of third-generation immigrants by the number of Asian grandparents in Table (\ref{regtab-bygrandparents}). The overall effect of state-level bias on the different type of Asian children is negative, however, they are also mostly statistically insignificant. I find that a one standard deviation increase in state-level bias is associated with a 69 percentage points decrease in self-reported Asian identity among Asian children that have three grandparents that are born in an Asian country.

@@

I present the results of estimating equation (\ref{eq:inter-interracial}) in Table (\ref{regtab-logit-02}). I find that a one standard deviation increase in bias increases the probability of having interracial parents by 3 percentage points. Moreover, I break down the analysis by the ethnicity of the couples. A one standard deviation increase in state-level bias is associated a 3 percentage points increase in the chances of a Asian husband marrying a White wife. A one standard deviation increase in state-level bias is associated a 4 percentage points increase in the chances of a Asian wife having a White husband. The fact that bias and interracial marriage are positively correlated could be a result of the fact that Asian immigrants in states with high bias might aim to decrease the likelihood that their children will display Asian ethnicity signals. For example, Asian women in high bias states might marry a non-Asian White husband, so their children will have a non-Asian last name.

I am also interested in investigating the relationship between state-level bias and migration. As the CPS does not report a person's birth state, I use the 2004-2021 Censuses to construct a sample of second-generation Asian immigrants \autocite{floodsarahIntegratedPublicUse2021}. I construct a mover variable to indicate whether these second-generation Asian immigrants have moved from their birth state to another state. For this purpose, I use the following models to estimate the relationship between state-level bias and migration:

@@

Moreover, \textcite{duncanIntermarriageIntergenerationalTransmission2011} show that reported Asian identification does not vary with who is the household respondent. Additionally, I present the main effect of self-reported Asian identity by the household respondent in Table (\ref{tab:hispbyproxy}). The main effect of the reported Asian identity of children is 93 percentage points when the mother is the proxy, 92 percentage points when the father is the proxy, and 96 percentage points when the child or another caregiver was the household respondent.\footnote{According to the Current Population Survey (CPS), a person can be the household respondent if they are at least 15 years old and have enough knowledge about the household. Thus, when the proxy is 'self,' the respondent is between the ages of 15 and 17.}

>>>>

I explore how individual characteristics and social attitudes toward Asians affect self-reported Asian identity. I use identity and ancestry information from the Current Population Survey (CPS) along with a proxy for bias using Harvard's Project Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes committed against Asians. \footnote{The IAT data is retrieved from Harvard's Project Implicit \autocite{greenwaldMeasuringIndividualDifferences1998}. The implicit bias toward minorities, as measured by IAT, is widely used by psychologists and is growing in use among economists. IAT scores were shown to be correlated with economic outcomes \autocite{chettyRaceEconomicOpportunity2020,gloverDiscriminationSelfFulfillingProphecy2017}, voting behavior \autocite{friesePredictingVotingBehavior2007}, and health \autocite{leitnerRacialBiasAssociated2016}.} I motivate my analysis with a simple model in the vein of \textcite{akerlofEconomicsIdentity2000}. The model makes an explicit path through which actions affect individuals' utility via their identity and introduces an externality where the actions of others---or prejudice---have different effects on a person's well-being and identity. Therefore, if a person can choose their identity credibly, and this choice is affected by the prejudice of others, then they will choose it to maximize their outcomes.

@@

Among individuals of Asian ancestry, I find that higher bias---against Asians---is correlated with a lower self-reported Asian identity among Asian immigrants. I find that an increase of one standard deviation in bias correlates with a statistically significant 9 percentage point decrease in the self-reported Asian identity among first-generation immigrants, a statistically insignificant 5 percentage point decrease among second-generation immigrants, and a statistically significant 8 percentage point decrease in the self-reported Asian identity among third-generation immigrants. Additionally, a one standard deviation increase in bias is correlated with a 5 percentage points (insignificant) drop in self-reported Asian identity among second-generation Asian children with both parents born in a Asian country, a 15 percentage point decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage point decrease in self-reported Asian identity among children of White fathers-Asian mothers. Consequently, as the more economically successful Asian immigrants---educated and wealthy immigrants---may self-report Asian identity, economic research using subjective ethnic measures will underestimate White-Asian gaps in the most biased states.

@@

I use Asian implicit association test data to construct a proxy of prejudice \autocite{greenwaldMeasuringIndividualDifferences1998}. This measure has been used in the social sciences, especially in psychology. Previous work has shown that IAT test scores are hard to manipulate \autocite{egloffPredictiveValidityImplicit2002}.

@@

Lastly, I incorporate data from the Uniform Crime Reports (UCR) to quantify hate crimes against Asians \autocite{ucrbook}. Hate crime data offers a tangible measure of racially motivated aggression and discrimination, which, when combined with implicit and explicit bias measures, allows for a fuller understanding of the landscape of prejudice across states. This combination of implicit and explicit bias measures, along with hate crime statistics, offers a multidimensional approach to understanding the nature and prevalence of racial prejudice.

Moreover, to reduce attenuation bias and measurement error, I follow \textcite{lubotskyInterpretationRegressionsMultiple2006} in constructing a composite bias measure using  the IAT, the ANES racial animus measure and hare crimes against Asians.\footnote{More on the method in the Data Online Appendix, see Section~\ref{sub:lw-bias}.} Figure (\ref{fig:skiniat}) shows a graphical representation of the bias measure over time in the most and least biased locations. Figure (\ref{fig:Asian-twostates}) shows a graphical representation of self-reported Asian identity in the two most and least biased locations. A lower score implies less bias, whereas a higher score implies higher racial animus. A one standard deviation increase in bias is equivalent to moving from Washington, DC, or Vermont to North Dakota in 2020. I also show the average bias over time in the maps in Figure (\ref{fig:skiniat-maps}) and the overall average from 2004 to 2021 in Figure (\ref{fig:iat-map-all}).
\section{Estimation and Results}\label{sec:empstrat}

To understand the association between Asian self-identity and bias, I estimate regressions of the following form for each generation $g$:

@@

Where $A_{ist}^g$ be the self-reported Asian identity of person $i$ in state $s$ at the time of interview $t$, let $Bias_{st}$ be the average bias in state $s$ at time $t$, $DadCollegeGrad_{ist}$, and $MomCollegeGrad_{ist}$ are indicator variables that are equal to one if the father or mother graduated from college, $Women_{ist}$ is an indicator variable for sex, and $X_{ist}$ is a vector of controls.\footnote{The controls include quartic age, fraction of population that is Asian in state $s$, type of parents (WA, AW, or AA), type of grandparents (AAAA, AAAW, etc.), and dummy variables the generation to which person $i$ belong.} Additionally, $\gamma_{rt}$ is region-time fixed effects that controls for region $\times$ year specific shocks.\footnote{I do not include state fixed effects because of lack of with-in state variation in bias.} The region $\times$ year also controls for systematic differences between regions in the overall Asian population and bias toward Asians, even if they vary over time. Throughout the analysis, I cluster the standard errors at the state level to account for correlation in the error term $\varepsilon_{ist}$ within a state, overtime.

Since the specification includes region $\times$ year, $\gamma_{rt}$, the $\beta_1^g$ coefficient summarizes individual's $i$ responsiveness to bias changes in the state which they live. In other words, $\beta_1^g$ captures the association between self-reported Asian identity and bias across states within a Census division region. Additionally, the $\gamma_{rt}$ fixed effects account for any regional and national trends in bias over time. Consequently, $\beta_1^g$ provide the correlation between self-reported Asian identity and bias above and beyond the national and regional trends in bias. If individuals in states within a region responded similarly to changes in bias, then $\beta_1^g$ will be equal to zero.

\section{Results}\label{sec:results}
The results from the regression framework described above provide consistent evidence aligning with the following findings. First, bias is negatively associated with self-reported Asian identity. Second, first- and second-generation Asian immigrant children of endogamous marriages' self-reported Asian identity are more negatively associated with bias.

I report the main results of estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}). I present the results of estimating the main specification for second-generation immigrants in panel (A) and for sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that bias and self-reported Asian identity are negatively associated. A one standard deviation increase in bias is associated with a 9 percentage points decrease in self-reported Asian identity. Among first- and second-generation Asian immigrants, a one standard deviation increase in bias is associated with 5 and 8 percentage points decrease in self-reported Asian identity. The coefficient is not statistically significant for first-generation, but the confidence interval is mostly in the negative territory. Finally, among third-generation Asian immigrants, a one standard deviation increase in bias is associated with a 8 percentage points decrease in self-reported Asian identity.

I report the results of the same regression but on sub-samples of second-generation immigrants by type of parents---interracial and endogamous parents---in Figure (\ref{plot01-regression-byparent}). I present the results of estimating the main specification on second-generation immigrants in panel (A) and on sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that children of interracial parents marriages are more influenced by bias. I find that a one standard deviation increase in bias is associated with a 5 percentage points decrease in self-reported Asian identity among children of endogamous parents---the estimate is statistically insignificant. However, a one standard deviation increase in bias is associated with a 15 percentage points decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage points decrease in self-reported Asian identity among children of White fathers-Asian mothers.

I also report the results of the regression on sub-samples of third-generation immigrants by the number of Asian grandparents in Table (\ref{regtab-bygrandparents}). The overall effect of bias on the different type of Asian children is negative, however, they are also mostly statistically insignificant. I find that a one standard deviation increase in bias is associated with a 69 percentage points decrease in self-reported Asian identity among Asian children that have three grandparents that are born in an Asian country.

@@

I present the results of estimating equation (\ref{eq:inter-interracial}) in Table (\ref{regtab-logit-02}). I find that a one standard deviation increase in bias increases the probability of having interracial parents by 4 percentage points. Moreover, I break down the analysis by the ethnicity of the couples. A one standard deviation increase in bias is associated with 1 percentage points decrease in the chances of a Asian husband marrying a White wife. A one standard deviation increase in bias is associated a 3 percentage points increase in the chances of a Asian wife having a White husband. The fact that bias and interracial marriage are positively correlated could be a result of the fact that Asian immigrants in states with high bias might aim to decrease the likelihood that their children will display Asian ethnicity signals. For example, Asian women in high bias states might marry a non-Asian White husband, so their children will have a non-Asian last name.

I am also interested in investigating the relationship between bias and migration. As the CPS does not report a person's birth state, I use the 2004-2021 Censuses to construct a sample of second-generation Asian immigrants \autocite{floodsarahIntegratedPublicUse2021}. I construct a mover variable to indicate whether these second-generation Asian immigrants have moved from their birth state to another state. For this purpose, I use the following models to estimate the relationship between bias and migration:

@@

Moreover, \textcite{duncanIntermarriageIntergenerationalTransmission2011} show that reported Asian identification does not vary with who is the household respondent. Additionally, I present the main effect of self-reported Asian identity by the household respondent in Table (\ref{tab:hispbyproxy}). The main effect of the reported Asian identity of children is 72 percentage points when the mother is the proxy, 72 percentage points when the father is the proxy, and 87 percentage points when the child or another caregiver was the household respondent.\footnote{According to the Current Population Survey (CPS), a person can be the household respondent if they are at least 15 years old and have enough knowledge about the household. Thus, when the proxy is 'self,' the respondent is between the ages of 15 and 17.}
